Capsule Based Aspect Extraction

### 2020-05-28 paper/main.tex
updated paper

\section{Introduction}
Aspect extraction is an important and challenging task in aspect-based sentiment analysis. For example, in the sentence "The beef was tender and melted in my mouth", the aspect term is "beef". Two sub-tasks are performed in aspects extraction: (1) extracting all aspects terms(e.g., "beef") from a review corpus, (2) clustering aspect terms with similar meaning into categories where each category represents a single aspect(e.g., cluster "beef", "pork", "pasta", and "tomato" into one aspect food) \cite{He2018ABAE}.

>>>>

\section{Introduction}
Aspect extraction is an important and challenging task in aspect-based sentiment analysis. For example, in the sentence "The beef was tender and melted in my mouth", the aspect term is "beef". Two sub-tasks are performed in aspects extraction: (1) extracting all aspects terms(e.g., "beef") from a review corpus, (2) clustering aspect terms with similar meaning into categories where each category represents a single aspect(e.g., cluster "beef", "pork", "pasta", and "tomato" into one aspect food) \cite{He2018ABAE}. in 2017 year, Unsupervised Aspect Extraction \cite{He2018ABAE} have become the dominant unsupervised approach for aspect extraction. In that work neural word embeddings map words with the same context to nearby points in the embedding space \cite{Mikolov2013W2V}. Then attention mechanism \cite{Bahdanau2015NMT} filter the word embeddings within a sentence and filtered words use to construct aspect embeddings. The training process for aspect embeddings is analogous to autoencoders, where dimension reduction use to extract the common factors among embedded sentences and reconstruct each sentence through a linear combination of aspect embeddings. The attention mechanism deemphasizes words that are not part of any aspects, allowing the model to focus on aspect words. That model call \textit{Attention-based Aspect Extraction} (ABAE).
